Untrusted B2B Collaboration using the Blockchain

### 2018-07-30 paper/paper.tex
Remove figure

\subsection{Contract Structure}
To realize the system, we use three kinds of smart contracts.
Firstly, each organization deploys one \emph{instance contract} per process instance.
It represents a public process of the organization and is called during the process execution whenever a catch or throw event is reached in the process instance.
In the case of catch events, an Ethereum event is logged to the blockchain for documentation.

@@

%TODO add a step in the diagram where other factory contracts are set
\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{fig/initialization.eps}
	\caption{A sequence diagram describing the initialization process for an organization.}
	\label{fig:initialization}
\end{figure}

Each organization needs to perform certain setup steps before the process execution.
The factory and access contracts corresponding to the process need to be deployed.
Additionally, the user-to-role and and task-to-role mappings have to be updated in the access contract (\texttt{giveRights} and \texttt{assignRole}, respectively), to allow verification of users during the process execution.
Lastly, the addresses of the factory contracts of all communication partners need to be linked in the own factory contract.
Figure \ref{fig:initialization} shows this setup sequence.

@@

%TODO add emit event in the diagram
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{fig/instance_creation.eps}
	\caption{A sequence diagram describing the process of creating a new process instance.}
	\label{fig:instance_creation}
\end{figure}

>>>>

\subsection{Contract Structure}

To realize the system, we use three kinds of smart contracts.
Firstly, each organization deploys one \emph{instance contract} per process instance.
It represents a public process of the organization and is called during the process execution whenever a catch or throw event is reached in the process instance.
In the case of catch events, an Ethereum event is logged to the blockchain for documentation.

@@

Each organization needs to perform certain setup steps before the process execution.
The factory and access contracts corresponding to the process need to be deployed.
Additionally, the user-to-role and and task-to-role mappings have to be updated in the access contract (\texttt{giveRights} and \texttt{assignRole}, respectively), to allow verification of users during the process execution.
Lastly, the addresses of the factory contracts of all communication partners need to be linked in the own factory contract.

@@

%TODO add emit event in the diagram
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{fig/instance_creation.eps}
	\caption{Example sequence diagram describing the creation of a new process instance in our choreography example.}
	\label{fig:instance_creation}
\end{figure}
